Econ Modeling One-pager

### 2016-08-08 NSF-ClusterGrant/EconOnePager.Rmd
Edited one-pager.

* Our collaborators in Portugal have completed a paper that uses the 
Cobb-Douglas APF in combination with co-integration techniques to understand
the relationship between energy and the economy in Portugal. 
At the Second Exergy Economics Workshop (Sussex, England)

**Additional paragraph here** (when Matt returns to radio contact) about future related 
integrating the paper described above with cointegration work that Tiago has done.  [Tiago is
a possible letter writer, so this makes a nice connection between the grant proposal and his
letter, and also demonstrates its usefulness for things being done beyond Calvin.]

>>>>

* Our collaborators in Portugal have completed a paper that employs the 
Cobb-Douglas APF in combination with statistical co-integration techniques to understand
the relationship between energy and the economy in Portugal [@jsantos2016]. 
Their next step is to switch from the Cobb-Douglas APF to the CES APF.
At the Second Exergy Economics Workshop (Sussex, England, July 2016), 
we made plans to collaborate. 
Our CES fitting techniques and resampling methods
will be applied to their cointegration analysis
to write a new paper analyzing the Portuguese economy.
